\label{fig:RXJ1131} Recovered lens model parameters for the RXJ1131 field. The LOS models are shown in blue, the Shear models in red, and the None models in green. We used MCMC to calculate the marginalized 1-D posterior probability distribution. The error bars have contributions from both measurement uncertainties and scatter from varying source positions and orientations of the main lens. A histogram of LOS/environment galaxies is shown along the bottom with the axis labels on the far right. Dark grey bins correspond to perturbers in the foreground of the main lens, and the light gray bins correspond to background perturbers. The x-axis shows the cutoff in $\Delta_3 x$. Any galaxy to the left of a point is treated exactly as a main plane (strong lens), while everything to the right is treated according to the model: the None models ignore the environment, the Shear models fit only a simple shear, and the LOS models use our framework using the tidal approximation. The leftmost point corresponds to using the shear approximation for all galaxies. If we went all the way to the right (there are many galaxies beyond the edge of what is shown) all of the galaxies would be taken into account exactly. Note that moving to the right corresponds to taking galaxies into account exactly that are farther away from the main lens. For all cuts on $\Delta_3 x$, the LOS models are unbiased. For $\Delta_3 x < 1e-4$, the scatter in all of the lens parameters is dominated by the observational uncertainties. The top right panel shows the Einstein radius parameter of the lens models. This shows the clearest difference between our LOS framework and traditional fitting techniques. The points on the left are higher than the truth for both the Shear and None models which in turn induces a bias in $h$ as shown in the top middle panel. This overestimate is due to ``external convergence'' and is accounted for in post processing. Because our LOS framework already includes the convergence in the LOS planes, we do not need to make this correction. At small values of $\Delta_3 x$, shown on the right of the plots, the fitted Einstein radius drops below the truth. This is because we have not included a void correction in the Shear and None models. This implies that for this lens, the correction due to voids is $~2\%$.
  
  